Elite individuals, insitutions, and economic growth accounting

### 2024-04-05 presentation/main.tex
maintaining old charts

>>>>

\begin{frame}{Imputing nulls}{Using XGBoost for better predictions}
    \begin{block}{Data is not missing at random}
        School completion data is only available for a maximum of 80 countries per year and has high variance in this availablility.
        This is the most limiting factor in the analysis.
    \end{block}

    \begin{block}{Predicting missing values}
        XGBoost is a tree-based model that has built-in null handling. I use the remaining variables to predict school completion rates.
        Achieves significantly higher accuracy than linear regression.
    \end{block}

\begin{frame}{Imputation results}
    \centering
    \includegraphics[width=\textwidth]{../build/xgboost.png}
\end{frame}
